# Check textdata

## namelist

```{r}
namelist_check <- 
    read_vc(namelist_path, root)
```

Are all codes unique per language?

```{r}
namelist_check %>% 
    count(code, lang) %>% 
    filter(n > 1) %>% 
    nrow == 0
```

No lines without names or shortname?

```{r}
namelist_check %>% 
    filter(is.na(name), is.na(shortname)) %>% 
    nrow == 0
```

All lines have a value for code and lang?

```{r}
namelist_check %>% 
    filter(is.na(code) | is.na(lang)) %>% 
    nrow == 0
```


Language statistics:

```{r}
namelist_check %>% 
    mutate(name = !is.na(name),
           shortname = !is.na(shortname)) %>% 
    group_by(lang) %>% 
    summarize(name = sum(name),
              shortname = sum(shortname))
```


## schemes

```{r}
schemes_check <- 
    read_vc(schemes_path, root)
```


Are all scheme codes unique?

```{r}
schemes_check %>% 
    count(scheme) %>% 
    filter(n > 1) %>% 
    nrow == 0
```

Which are the represented programmes (projects)?

```{r}
schemes_check %>% 
    distinct(programme)
```

Are all `attribute_2` values of the MNE programme known environmental pressures codes?

```{r}
schemes_check %>% 
    filter(programme == "MNE") %>% 
    distinct(attribute_2) %>% 
    .$attribute_2 %in% read_env_pressures()$ep_code %>% 
    all
```


## scheme_types

```{r}
scheme_types_check <- 
    read_vc(scheme_types_path, root)
```


No double combinations occur?

```{r}
scheme_types_check %>% 
    count(scheme, type) %>% 
    filter(n > 1) %>% 
    nrow == 0
```

All occurring schemes are present in `schemes`?

```{r}
scheme_types_check %>% 
    .$scheme %in% schemes_check$scheme %>% 
    all
```

All occurring types are known types?

```{r}
scheme_types_check %>% 
    .$type %in% read_types()$type %>% 
    all
```

When a scheme-type combination has a typegroup, is this always the case for all types of the concerned scheme?

```{r message=FALSE}
scheme_types_check %>% 
    group_by(scheme) %>% 
    summarise(nr_entries = sum(!is.na(typegroup))) %>% 
    filter(nr_entries > 0) %>% 
    inner_join(scheme_types_check) %>% 
    filter(is.na(typegroup)) %>% 
    nrow == 0
```



